### 2024-07-30 paper.tex
write about m^2 thing

>>>>

\section{A different variety}
Define \(R = \{(X, \mathfrak{b}_1, \mathfrak{b}_2) : X \in \mathfrak{b}_1 \land u(X) \in \mathfrak{b}_2\} \subseteq \mathcal{S}_{m,n}' \times \mathcal{B}_{m + n} \times \mathcal{B}_m\).
We can obtain a subvariety of \(R\) by requiring that \(u(X)\) is in some fixed similarity class.
(TODO: why is this a subvariety?  Is it?  Is this even the right way of explaining the significance of the \(m^2\)?)
We expect that each of these subvarieties is an irreducible component of dimension \(m^2\).
We will verify these things using our prvious computations of springer fibers.
